\LARGE \bf Reactive Trajectory Planning and Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-04-09 root.tex
remove some lines

Section \ref{sec:systemarchirecture} describes the architecture of our system and 
other subsystems that interact with our system.
Section \ref{sec:pathmanager} describes the high-level Path Manager that calls the trajectory planner as necessary to 
exhibit reactive behavior and stop for pedestrians that may appear on the road.
Section \ref{sec:trajectoryplanning} describe trajectory planning, where we start with a 2D path, and generate a trajectory that satisfies maximum velocity, acceleration and jerk constraints. 
%We explain how we pass through intersections, turns in the road and planned stops at the stop signs.
We then describe extensions to trajectory planner that handle reactivity to pedestrians in the environment. 
Once the trajectory plan is formulated, we send the reference signal to the controllers that govern steering, braking, and engine speed.
This is the trajectory tracking problem, which is discussed in Section \ref{sec:trajectorytracking},
followed by conclusions and future extensions.
% tracking

>>>>

Section \ref{sec:systemarchirecture} describes the architecture of our system and 
other subsystems that interact with our system.
Section \ref{sec:pathmanager} describes the high-level Path Manager that calls the trajectory planner as necessary to 
exhibit reactive behavior and stop for pedestrians that may appear on the road.
Section \ref{sec:trajectoryplanning} describes trajectory planning, where we generate a trajectory that satisfies maximum velocity, acceleration and jerk constraints. 
%We explain how we pass through intersections, turns in the road and planned stops at the stop signs.
%We then describe extensions to trajectory planner that handle reactivity to pedestrians in the environment. 
Once the trajectory plan is formulated, we send the reference signal to the controllers that govern steering, braking, and engine speed.
This is the trajectory tracking and is discussed in Section \ref{sec:trajectorytracking},
followed by conclusions and future extensions.
% tracking
